\documentclass[10pt,letterpaper]{resume}

\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\name{Ryan Wicks}
\degree{BSc.H., MSc., Ph.D}
\address{640 Royal Fern St. \\Waterloo, ON, N2V 2P6}
\phone{(226) 750-7063 }
\email{ryancwicks@gmail.com}


\begin{document}
\maketitle

\section{Experience}

\entry 2012/07-Present @ Waterloo, ON. 2G Robotics Inc.| Chief Scientist/Developer
\textit{\\2G Robotics provides a line of underwater laser metrology equipment and imaging solutions to the offshore oil and gas industries.}
\begin{itemize}
\item Current role as Chief Scientist involves leading a small team of scientists developing next generation underwater imaging products, image processing algorithms and improving the state of the art in optical calibration for underwater metrology.
\item Initial role as primary hardware developer led to the development of a line of underwater laser scanners, cameras and stereo vision systems. Responsible for hardware development (high speed digital and analog electronics design through system level programming and algorithm development).
\item Managed several high profile deployments with large oil and gas customers that have led to equipment profiles in several trade journals and the adoption of laser scanning as a standard offshore metrology tool.
\item Mentored new group members and worked in small teams to develop state of the art underwater metrology equipment.
\item Wrote several white papers for internal and external use. Currently hold 1 patent.
\end{itemize}

\entry 2005/09-2012/07 @ Vancouver, BC. Quantum Materials Group| Researcher
\textit{\\The Quantum Materials Group combines expertise in materials preparation and spectroscopy to further our understanding of correlated electron systems.}
\begin{itemize}
\item Designed and managed thin film preparation and x-ray photoelectron spectroscopy facility. Enabled UBC researchers and their collaborators to quickly prepare and characterize their samples while saving ~\$10K+ per group per year on external lab costs.
\item Mentored new group members and helped them develop their research goals.
\item Published five research papers in high impact, peer-reviewed journals, wrote two dissertations and presented my work to both technical and general audiences.
\end{itemize}

\entry 2005/09-2012/05 @ Vancouver, BC. UBC Department of Physics/Engineering Physics| Teaching Assistant
\textit{\\The UBC department of physics has a strong commitment to developing effective teaching methods through the Carl Wieman Science Education Initiative.}
\begin{itemize}
\item Primary TA for all upper year electronics, embedded design, signal processing and data analysis courses in the Physics Department.
\item Acted as a mentor in upper year design Engineering Physics projects, leading teams of students from vision to prototype.
\end{itemize}

\entry 2011 @ Vancouver, BC. West Coast Medical Devices| Chief Technology Officer
\textit{\\WCMD was an early stage medical devices company developing a wound risk reducing air mattresses for the home care market.}
\begin{itemize}
\item Developed a technology with a \$300M addressable market that could help prevent costly pressure wounds, improving quality of life and savings thousands per year per patient in treatment costs.
\item Performed market research, patent reviews and financial modeling while developing the business model.
\item Made it to second round of the BC Innovation Council New Ventures Competition.
\end{itemize}

%\entry 2001/05-2002/06 @ Canada. Department of National Defense| Officer In Training
%\textit{\\Officer in the Army Signals Corp}
%\begin{itemize}
%\item  Received training in leadership and management, and practiced it under extreme conditions.
%\end{itemize}

\section{Selected Projects and Skills}

\entry  . ULS500 Pro Development| Core Team Member
\textit{\\Played central role in initial product definition, development and subsequent improvements to 2G Robotics flagship product.}
\begin {itemize}
\item System Design, Multi-Threaded C++ Development, Algorithm Development, High-Speed, Digital Electronics Design, Firmware Development (C), TCP/IP Sockets, Protocol Development, Serial Communication, Real Time Data Processing, API Development, Distributed Computing, GUI Development
\end {itemize}

\entry . Underwater Camera Modelling| Sole Contributor
\textit{\\Developed a model to account for the effect of changing water conditions on camera based laser scanner calibration. Implemented these changes to the real time data processing code of the ULS500 line of underwater laser scanners. }
\begin {itemize}
\item Camera Model Development, C++ Development, Python Development, Algorithm Development, Real Time Data Processing
\end {itemize}

\entry . Laser Scanner Calibration and Verification| Sole Contributor
\textit{\\Responsible for many improvements and enhancements over several years in 2G Robotics laser scanner and camera calibration procedures, resulting in the most accurate underwater laser scanners in the world.}
\begin {itemize}
\item Camera Modeling, Image Processing, C++ Development, QUI Development (Windows), Algorithm Development, Non-linear Minimization (CERES), Motion Capture, Rigid Body Transforms, Python Development, 3D Modelling
\end {itemize}

\entry . 3D Animation Plugin Development| Initial Contributor
\textit{\\Developed initial version of plugin to allow users of the open source software CloudCompare to generate movies from 3D point clouds}
\begin {itemize}
\item 3D Modelling, C++ Development, Rigid Body Transforms, GUI Development (Linux and Windows)
\end {itemize}

\entry . Field Calibration of Vehicle Mounted Laser System| Core Team Member
\textit{\\Developed system to allow field calibrations of vehicle mounted laser scanners.}
\begin {itemize}
\item Image Processing, Real Time Data Processing, C++ Development, Rigid Body Transforms, Web Development (Javascript and HTML)
\end {itemize}

\entry . Algorithm Optimization for High Speed Image Analysis| Sole Contributor
\textit{\\Improved the data acquisition speed of ULS500 Pro from 25 fps to greater than 75fps through algorithm enhancements, incorporating multiple threads and hardware optimization.}
\begin {itemize}
\item Multi-Threaded C++ Development, Hardware Optimization, TCP/IP Socket Communication, Distributed Computing, Algorithm Development, Real-Time Data Processing
\end {itemize}

\section{Education}

\entry 2007/09-2012/07 @ Vancouver, BC. Ph.D in Experimental Condensed Matter Physics| UBC
\begin{itemize}
\item Directed my own research project after my co-supervisor left the university.
\item Dissertation on the growth and properties of ferromagnetic semiconductors.
\end{itemize}

\entry 2005/09-2007/09 @ Vancouver, BC. MSc. in Experimental Condensed Matter Physics| UBC
\begin{itemize}
\item Dissertation on tuning the properties of high temperature superconductors.
\end{itemize}

\entry 2002/09-2005/05 @ Kingston, ON. BSc.H. in Physics| Queen's University
\begin{itemize}
\item Honours thesis on acoustic lasers-developed theoretical model and studied it numerically.
\end{itemize}

\section{Volunteering}

\entry 2015-2016 @ Waterloo, ON. KwartzLab| Secretary
\begin {itemize}
\item Member of board of directors at Kwartzlab, the Kitchener/Waterloo Maker space.
\end {itemize}

\entry 2007-2012 @ Vancouver, BC. Advanced Materials and Process Engineering Lab| Safety Committee Member
\begin{itemize}
\item Part of team responsible for the safe operation of multi-disciplinary laboratory.
\item Managed risks associated with facilities ranging from steel processing to class 1000 cleanrooms.
\end{itemize}

\entry 2006-2010 @ Vancouver, BC. UBC Sailing Club| Monohull Fleet Captain
\begin{itemize}
\item Responsible for maintenance, procurement and safe use of the monohull sailing fleet, consisting of 23 vessels, worth ~\$250K, and used by ~500 members.
\item Supervisor of 1 full time employee and two volunteer maintenance personnel.
\end{itemize}

%\entry 2008-2009 @ Vancouver, BC. Eburne Landing Housing Co-Operative| Vice-President, Board of Directors
%\begin{itemize}
%\item Responsible for the co-op's outside communications to our management company, creditors and contractors  leading up to a \$2M building remediation.
%\end {itemize}

%\entry 2005-2009 @ Vancouver, BC. Let's Talk Science| Outreach Volunteer
%\begin{itemize}
%\item Educated school age children about science through public outreach activities and curriculum appropriate in class demonstrations.
%\end{itemize}

\section{Interests}
Ultra running, adventure racing, "making"
\end {document}
