\documentclass[letterpaper,12pt]{article}

\usepackage{fancyhdr,lastpage,calc}
\usepackage[document]{ragged2e}

\setlength\RaggedRightRightskip{0pt plus 1cm}
\setlength\RaggedRightParindent{12pt}

\setlength\voffset{-0.95in}
\setlength\hoffset{-0.15in}
\setlength\oddsidemargin{0in}
\setlength\marginparwidth{0in}
\setlength\marginparsep{0.75in}
\setlength\topmargin{0.75in}
\setlength\textheight{8.5in}
\setlength\textwidth{6.7in}

%\setcounter{page}{7}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{\large{Ryan Wicks}}
\fancyhead[C]{\large{\emph{Curriculum Vitae}}}
\fancyhead[R]{\large Page \thepage\, of \pageref{LastPage}}
\fancyfoot{}
%\fancyfoot[C]{Page \thepage} % \ of \pageref{LastPage}}
\setlength\headheight{18pt}
\renewcommand\headrulewidth{1pt}
%\renewcommand\footrulewidth{0pt}

\makeatletter
\renewcommand\section{\@startsection
{section}{1}{-12pt}
{\baselineskip}
{\baselineskip}
{\normalfont\large\textbf}}
\makeatother

\makeatletter
\renewcommand\subsection{\@startsection
{subsection}{2}{12pt}
{-\baselineskip}
{0pt}
{\normalfont\normalsize\textbf}}
\makeatother

\setcounter{secnumdepth}{-2}
\begin{document}
\begin{center}{ \addvspace{0.3cm}   \Large{Ryan Wicks, BSc.H., MSc., Ph.D Candidate} \\ \addvspace{0.5cm} \normalsize{3559 19th Avenue W. \\ Vancouver, BC, V6S 1C3 \\ (604) 266-7515\\ryancwicks@gmail.com}} \end{center} \addvspace {0.5cm}

\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Education}\\ \hline \end{tabular}
\linebreak
\linebreak
\normalsize \textbf{Ph.D. in Physics} University of British Columbia, Vancouver, BC. (In Progress)\\
$ $\linebreak
\normalsize \textbf{MSc. in Physics} University of British Columbia, Vancouver, BC. (2007)\\
 $ $\linebreak
\normalsize \textbf{BSc. (Honours) Subject of Specialization in Physics} Queen's University, Kingston, ON. (2005)\\
$ $\linebreak

\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Research Experience}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf{Graduate Work with Dr. Andrea Damascelli:} I am currently completing a Ph.D. degree in the Quantum Materials Laboratory at the University of British Columbia. My research focuses on the epitaxial growth and characterization of transition metal and rare earth oxide films. In this role, I have utilized the technique of molecular beam epitaxy to prepare my samples, and a variety of experimental tools to characterize and study the prepared films. These include x-ray diffraction, x-ray reflectivity, reflection high energy electron diffraction, low energy electron diffraction, SQUID magnetometry, x-ray absorption spectroscopy and photoelectron spectroscopy. I also designed, built and commissioned a custom ultra high vacuum growth and characterization system to perform my experiments. (2005 to present) \\
$ $\linebreak
\noindent \textbf{Visitor in the Group of Dr. Hao Tjeng:} I visited Dr. Tjeng's group at the University of Cologne, Germany, for two and a half months to gain experience growing thin films of EuO using the distillation method they developed. I assisted them in their study of Eu rich, as well as Gd doped EuO films, and undertook my own project involving N doped EuO films. (2009) \\
$ $\linebreak
\noindent \textbf{Synchrotron Experience:} I have performed angle resolved photoemission experiments at the Synchrotron Radiation Center in Wisconsin as well as x-ray absorption and photoemission experiments on films prepared \textit{in situ} at the National Synchrotron Radiation Research Center in Taiwan.\\
$ $\linebreak
\noindent \textbf{Summer Research Assistant in the Group of Dr. Binu Mukerjee:} This was a summer position at the Ferroelectrics lab at the Royal Military College of Canada. My duties included setting up and commissioning a laser interferometer for measuring the strain of piezoelectric samples, running strain and polarization experiments on these samples, and analyzing the data from these experiments. (Summer 2004)\\
$ $\linebreak

\noindent\Large \begin{tabular}{|p{12cm}|} \hline \textbf{Academic/Teaching Experience}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\textbf{Teaching Assistant:} I have run tutorials, laboratories and prepared course material for the following classes at the University of British Columbia:

\begin{itemize}
\item PHYS319 - Micro-controller Based Instrument Design (Laboratory)(Spring Term 2012)
\item PHYS309 - Electronics and Data Acquisition (Laboratory)(Fall Term 2006, 2007, 2008, 2009, 2010, 2011)
\item ENPH253 - Introduction to Instrument Design (Laboratory (Summer Term 2008, 2011)
\item PHYS153 - Elements of Physics (Laboratory)(Spring Term 2008, 2012)
\item PHYS102 - Electricity, Light and Radiation (Laboratory)(Fall Term 2007, 2008)
\item PHYS101 - Energy and Waves (Tutorial)(Spring and Summer Terms 2006)
\item PHYS100 - Introductory Physics (Tutorial)(Fall Term 2005)
\end{itemize}
\noindent \textbf{Let's Talk Science Volunteer:} This NSERC funded program involves teaching public school children about curriculum appropriate topics in science and other public outreach activities. The aim of the program is to promote interest in science and to dispel misconceptions about science and scientists. (2005 to 2009)\\
$ $\linebreak
\textbf{Marker:} I have marked assignments and projects for the following classes at Queen's University:

\begin {itemize}
\item PHYS 211/212 - Applied Physics (2003)
\item PHYS 242/342 - Relativity and Quantum Mechanics (2004)
\end {itemize} 

%\noindent \textbf {Army Cadet Instructor:} I was an instructor for the Royal Canadian Army Cadet youth organization, where I taught a wide variety of topics from the Army Cadet Training syllabus to 12-18 year olds. (1999-2001)\\
$ $ \linebreak


\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Non-Academic Experience}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf{CTO of West Coast Medical Devices:} I was part of a management team that developed a business plan around building high end, adaptive medical air mattresses for people with long term disability. This plan was generally well received, receiving top marks in APSC 541/BAEN506/507 - Technology Entrepreneurship course at UBC, making it to the second round of the British Columbia Innovation Council business plan competition and generating positive feedback from occupational therapists, doctors and patients. The business has not been carried past the planning stage since it was unlikely to receive funding in the current Vancouver venture capital environment.  (2011)\\
$ $ \linebreak
\noindent \textbf{Safety Committee Member, Advanced Materials and Process Engineering Laboratory, UBC}: Responsible for ensuring the continued safe operation of a multi-disciplinary research institute by setting safety policy and performing routine inspections. The facilities broad range of research activities introduce a variety of hazards that must be dealt with, from hazards associated with steel processing research to ensuring proper chemical storage in a class 1000 cleanroom facility. (2007-Present)\\
$ $ \linebreak
\noindent \textbf{Proprietor of Mikazzy Industries:} I am the sole proprietor of Mikazzy Industries, a company that sells small stepper motor control systems for the hobby CNC market and also offers custom electrical and mechanical design services. (2011-Present)  \\
$ $ \linebreak
\noindent \textbf{Monohull Fleet Captain, UBC Sailing Club:} Responsible for maintenance, procurement and safe use of the dinghy fleet at the UBC Sailing club (23 vessels used by approximately 500 members). (2006 to 2010)\\
$ $ \linebreak
 \textbf{Vice-President, Board of Directors, Eburne Landing Housing Co-Operative:} Responsible for the co-op's outside communications to management companies, creditors and contractors. (2008 to 2009) \\
$ $\linebreak
\noindent \textbf{Officer in the Canadian Forces}: Officer in Signals Corps. Honourably discharged. (2000 to 2001)\\
$ $\linebreak


\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Publications}\\ \hline \end{tabular} \normalsize
\linebreak
\begin{itemize}
\item{Altendorf, S.G., Hollmann, N., Sutarto, R., Caspers, C., \textbf{Wicks, R.C.}, Chin, Y.- Y., Hu, Z., Kierspel, H., Elfimov, I.S., Hsieh, H.H., Lin, H.-J., Chen, C.T., and Tjeng, L.H. "Spectroscopic observation of strain-assisted Tc enhancement in EuO upon Gd doping". Physical Review B (Accepted) (2012)}
\item {\textbf{Wicks, R.}, Altendorf, S.G., Caspers, C., Sutarto, R., Tjeng, L.H., and Damascelli, A.
"NO-assisted molecular-beam epitaxial growth of nitrogen substituted EuO", Applied Physics Letters (Accepted) (2012)}
\item{Ingle, N.J.C., Yuskauskas, A., \textbf{Wicks, R.}, Paul, M., and Leung, S., "Determining the epitaxial influence on the structure of thin films by \textit{in situ} diffraction techniques",  Journal of Physics D: Applied Physics., \textbf{43}: 133001 (2010)}
\item{\textbf{Wicks, R.}, and Ingle, N.J.C., "Characterizing the detection system nonlinearity, internal inelastic background, and transmission function of an electron spectrometer for use in x-ray photoelectron spectroscopy", Review of Scientific Instruments., \textbf{80}: 053108 (2009) }   
\item{Ren W., Han L., \textbf{Wicks R.}, Yang G., Mukherjee B.K., ''Electric field induced phase transitions of  \verb|<001>|-oriented $Pb(Mg_{1/3}Nb_{2/3})O_3-PbTiO_3$ single crystals", Proceedings of the SPIE., \textbf{5761}, 272-278 (2005)}
\end{itemize}
$ $\\

\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Theses}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf{Ph.D} - Molecular Beam Epitaxy of Magnetic Oxynitride Films (in preparation)\\
$ $ \linebreak
\noindent \textbf{MSc.} - The Growth of Novel Oxide Thin Films (2007)\\
$ $ \linebreak
\noindent \textbf{BSc.H.} -  The Acoustic Laser (2005)\\
$ $ \linebreak
$ $\\

\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Awards}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf {The Pacific Century Graduate Scholarship.} Awarded 2010 ($\$10000$)\\
$ $ \linebreak
$ $\noindent \textbf {David W. Strangway Fellowship.} Awarded 2010 ($\$800$)\\
$ $ \linebreak
$ $\noindent \textbf {University of British Columbia University Graduate Fellowship.} Awarded 2010 ($\$6200$)\\
$ $ \linebreak
$ $\noindent \textbf {University of British Columbia International Mobility Award.} Awarded 2009 ($\$1500$)\\
$ $ \linebreak
\noindent \textbf {University of British Columbia University Graduate Fellowship.} Awarded 2007-2008. ($\$16000$)\\
$ $\linebreak
\noindent \textbf {University of British Columbia Graduate Entrance Scholarship.} Awarded 2005. ($\$3685$)\\
$ $\linebreak
\noindent \textbf {National Sciences and Engineering Research Council Undergraduate Student Research Award.} Held at the Royal Military College of Canada. Awarded 2004. ($\$4500$)\\
$ $ \linebreak

%temporary, to make new page.
%\pagebreak[4]
\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Academic Honours}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf {Dean's List:} Royal Military College (2002); Queen's University (2003, 2004, 2005)\\
%$ $ \linebreak


%\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{Research Interests}\\ \hline \end{tabular} \normalsize
%\linebreak
%\begin{itemize}
%\item Materials Science
%\item Photoelectron Spectroscopy
%\item Molecular Beam Epitaxy
%\item Magnetic Materials
%\item Strongly Correlated Systems

%\end{itemize}
%\addvspace {0.6cm}

\noindent \Large \begin{tabular}{|p{12cm}|} \hline \textbf{References}\\ \hline \end{tabular} \normalsize
\linebreak
\linebreak
\noindent \textbf{Dr. Andrea Damascelli}, Professor of Physics at UBC, Research supervisor, damascelli@phas.ubc.ca, 604-822-4750 \\
$ $ \linebreak
\noindent \textbf{Doug Wong}, Head of Science Technical Services at UBC, Co-worker, dwong@phas.ubc.ca, 60-822-8210 \\
$ $ \linebreak
\noindent \textbf {Dr. Jon Nakane}, Engineering Physics Lab Co-ordinator at UBC, Co-worker, jnakane@phas.ubc.ca, 604-822-2110\\
$ $ \linebreak
\noindent \textbf {Dr. Andrzej Kotlicki}, Lecturer/Research Associate at UBC, Co-worker, kotlicki@phas.ubc.ca, 604-822-3645\\

\end {document}